Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
a bit more progress
acm stuff
KC almost finishes his part

\newtheorem{theorem}{Theorem}[]
\newtheorem{proposition}{Proposition}[]
\newtheorem{corollary}{Corollary}[]
\newtheorem{definition}{Definition}

\newcommand{\GTLC}{\texttt{GTLC+}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
\newcommand{\stxrulecont}[1]{& | & #1 & \\}
\newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
\newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
\newcommand{\plus}[0]{+}
\newcommand{\judgetype}[3]{#1 \vdash #2 : #3}
\newcommand{\judgeType}[2]{#1 : #2}
\newcommand{\judgeTypeFT}[3]{#1 : #2 \Longrightarrow #3} % FT = From To
\newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
\newcommand{\lazyD}{$\mathtt{Lazy D}$}
\newcommand{\eager}{$\mathtt{Eager}$}
\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
\newcommand{\TOOdyn}[0]{\star}
\newcommand{\TOOpre}[1]{#1}
\newcommand{\POOunit}[0]{\mathtt{Unit}}
\newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
\newcommand{\POOprod}[2]{#1 \times #2}
\newcommand{\POOsum}[2]{#1 \plus #2}
\newcommand{\eOOvar}[1]{#1}
\newcommand{\eOOsole}[0]{\mathtt{unit}}
\newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
\newcommand{\eOOapp}[2]{#1 \; #2}
\newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
\newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
\newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
\newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
\newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\oOOinj}{\mathtt{dyn}}
\newcommand{\oOOsole}{\mathtt{unit}}
\newcommand{\oOOfun}{\mathtt{fun}}
\newcommand{\oOOcons}{\mathtt{cons}}
\newcommand{\oOOinl}{\mathtt{inl}}
\newcommand{\oOOinr}{\mathtt{inr}}
\newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
\newcommand{\vOOtt}[0]{\mathtt{unit}}
\newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
\newcommand{\vOOinl}[1]{\mathtt{inl}\;#1}
\newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D blame calculus on space-inefficient CEK
\newcommand{\judgeDBreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
\newcommand{\judgeDBreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDBeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
\newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{D} & #2 & #3\\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longrightarrow_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longrightarrow_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{#2 \Downarrow_{\mathcal{S}(#1)} #3}
\newcommand{\redruleS}[3]{#1 & \longrightarrow_{\mathcal{S}(C)} & #2 & #3\\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hyper-coercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}

@@

\begin{definition}[Cast Representation]
	A cast representation has four interface functions:
	\begin{description}
		\item[$ id(T) $] constructs an identity cast
		\item[$ seq(c_1,c_2) $] composes two casts
		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
		\item[$ applyCast(c,v) $] applies a cast onto a value
	\end{description}
\end{definition}

@@

\section{\lazyD\ Cast Representations}

In this section we describe a subset of SR, where all 
elements implement the \lazyD{} blame strategy. We will show in 
\secref{sec:LDHC-correct} that the \lazyD\ HC is a member of this set.

\begin{definition}[Surely \lazyD]
	A cast representation is surely \lazyD\ if
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
				 $ \judgeTypeFT{c_1}{T_1}{T_2} $, and
				 $ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(seq(c_1,c_2),v) = 
			   applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
		where 
		\[
		\begin{array}{rcl}
			\rOOsucc{v} >>= f & = & f(v) \\
			\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
		\item If $ v : P $,
		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
		= applyCast(cast(P,l,Q),v) $
		\item If $ v : P $,
		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
		\item
		$ 
		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

@@

\subsection{All surely \lazyD{} cast representations are equivalents}

With the properties of surely \lazyD{} CR, it is straightforward to proof that 
all machines instantiated with these CRs bi-simulate each other. 
The relation connecting states of these machines ($ s \approx s $) is derived 
from the definition of states. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

The relations between continuations, pre-continuations, enviroments, values, 
cast results are also derived from their definitions. But the relation for 
casts is special. \begin{gather*}
\inference{
}{
	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
}
\quad
\inference{
}{
	id_1(T) \approx id_2(T)
}
\quad
\inference{
	c_1 \approx c_2 &
	c_3 \approx c_4
}{
	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
}
\end{gather*}

\begin{proposition}[Strong Bi-simulation of surely \lazyD{} Cast 
Representations]
	If 
	\begin{itemize}
		\item $ C_1 $ and $ C_2 $ are surely \lazyD,
		\item $ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $
		\item $ s_1 \approx s_3 $
		\item $ \judgeSreduce{C_1}{s_1}{s_2} $
	\end{itemize}
	then there exists an $ s_4 $ such that
	\begin{itemize}
	\item $ s_3 \approx s_4 $ and
	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
	\end{itemize}
\end{proposition}

The key idea of this proof is using the property (2) of surely 
\lazyD{} CR to undo sequencing. Property (3)-(11) cover all possibly uses of $ 
cast(T,l,T) $.

As a corollary, machines instantiated with proper cast representations are 
equivalent when used as interpreters.

\begin{proposition}[Equivalence of surely \lazyD{} Cast Representations]
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are surely \lazyD,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}

\subsection{Relating Surely \lazyD\ Cast Representations to $ \mathcal{D} $}

Now we proof that all $ 
\mathcal{S}(\cdot) $ instantiated with a surely \lazyD{} CR weakly bi-simulate 
the machine $ \mathcal{D} $.

\todo[inline]{list of cast}

\begin{proposition}[proper cast represenations are correct]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a surely 
	\lazyD{} cast 
	representation
	\[
	\judgeDBeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{proposition}

\section{Correctness Proof of \lazyD{} Hyper-coercions}
\label{sec:LDHC-correct}

To show that \lazyD\ HC is correct, we first show it is surely \lazyD, then 
uses the theorems in \secref{sec:CEKS} to prove our goals.

\figref{hc-applyCast} defines $ applyCast $, the last interface function.
We generalize shallow-consistency to middles and values $ m \smile v $ in the 
natural way.
Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.

@@

\begin{lemma}[\lazyD{} Hyper-coercion is surely \lazyD]
	See appendix.
\end{lemma}

\begin{theorem}[\lazyD{} hyper-coercion is correct]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeDBeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}

>>>>

\newtheorem{theorem}{Theorem}[]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{proposition}{Proposition}[]
\newtheorem{definition}{Definition}

\newcommand{\GTLC}{\texttt{GTLC+}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
\newcommand{\stxrulecont}[1]{& | & #1 & \\}
\newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
\newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
\newcommand{\plus}[0]{+}
\newcommand{\judgetype}[3]{#1 \vdash #2 : #3}
\newcommand{\judgeType}[2]{#1 : #2}
\newcommand{\judgeTypeFT}[3]{#1 : #2 \Longrightarrow #3} % FT = From To
\newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
\newcommand{\lazyD}{$\mathtt{Lazy D}$}
\newcommand{\eager}{$\mathtt{Eager}$}
\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
\newcommand{\TOOdyn}[0]{\star}
\newcommand{\TOOpre}[1]{#1}
\newcommand{\POOunit}[0]{\mathtt{Unit}}
\newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
\newcommand{\POOprod}[2]{#1 \times #2}
\newcommand{\POOsum}[2]{#1 \plus #2}
\newcommand{\eOOvar}[1]{#1}
\newcommand{\eOOsole}[0]{\mathtt{unit}}
\newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
\newcommand{\eOOapp}[2]{#1 \; #2}
\newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
\newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
\newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
\newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
\newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\oOOinj}{\mathtt{dyn}}
\newcommand{\oOOsole}{\mathtt{unit}}
\newcommand{\oOOfun}{\mathtt{fun}}
\newcommand{\oOOcons}{\mathtt{cons}}
\newcommand{\oOOinl}{\mathtt{inl}}
\newcommand{\oOOinr}{\mathtt{inr}}
\newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
\newcommand{\vOOtt}[0]{\mathtt{unit}}
\newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
\newcommand{\vOOinl}[1]{\mathtt{inl}\;#1}
\newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D blame calculus on space-inefficient CEK
\newcommand{\judgeDBreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
\newcommand{\judgeDBreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDBeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
\newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{D} & #2 & #3\\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longrightarrow_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longrightarrow_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{#2 \Downarrow_{\mathcal{S}(#1)} #3}
\newcommand{\redruleS}[3]{#1 & \longrightarrow_{\mathcal{S}(C)} & #2 & #3\\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hyper-coercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvDS}[3]{#2 \approx_{\mathcal{DS}} #3}

@@

\begin{definition}[Cast Representation]
	A cast representation is a set indexed by two types and has four interface 
	functions:
	\begin{description}
		\item[$ id(T) $] constructs an identity cast
		\item[$ seq(c_1,c_2) $] composes two casts
		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
		\item[$ applyCast(c,v) $] applies a cast onto a value
	\end{description}
\end{definition}

\begin{definition}[Monoidic Cast Representation]
	A cast representation is monoidic if 
	for all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

@@

\section{Correctness Proof of \lazyD{} Hyper-coercions}

\subsection{\lazyD\ Cast Representations}

In this section we describe a subset of SR, where all 
elements implement the \lazyD{} blame strategy. We will show in 
Subsection~\ref{sec:LDHC-correct} that the \lazyD\ HC is in this subset.

\begin{definition}[Surely \lazyD\ Cast Representation]
	A cast representation is surely \lazyD\ if
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
				 $ \judgeTypeFT{c_1}{T_1}{T_2} $, and
				 $ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(seq(c_1,c_2),v) = 
			   applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
		where 
		\[
		\begin{array}{rcl}
			\rOOsucc{v} >>= f & = & f(v) \\
			\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
		\item If $ v : P $,
		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
		= applyCast(cast(P,l,Q),v) $
		\item If $ v : P $,
		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
		\item
		$ 
		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

@@

\subsection{Relating All Surely \lazyD{} Cast Representations}

With the properties of surely \lazyD{} CR, it is straightforward to proof that 
all machines instantiated with these CRs bi-simulate each other. 
The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states. We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

The relations between continuations, pre-continuations, enviroments, values, 
cast results are also derived from their definitions. But the relation for 
casts is special: \begin{gather*}
\inference{
}{
	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
}
\quad
\inference{
}{
	id_1(T) \approx id_2(T)
}
\quad
\inference{
	c_1 \approx c_2 &
	c_3 \approx c_4
}{
	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
}
\end{gather*}

\begin{proposition}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
	$ s_1 \approx s_3 $,
	$ \judgeSreduce{C_1}{s_1}{s_2} $,
	then there exists an $ s_4 $ such that
	\begin{itemize}
	\item $ s_2 \approx s_4 $ and
	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
	\end{itemize}
\end{proposition}
\begin{proof}
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} CR, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
	\label{thm:surely-lazyD-eqv}
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are surely \lazyD cast representations,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}
\begin{proof}
	Immediately from Proposition~\ref{thm:CEKS-bisim}.
\end{proof}

\subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}

So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
each other. But this does not mean they respect the semantics of the \lazyD{} 
Blame Calculus. We solve prove this part in this subsection.

The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the 
definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
between continuations, between values, and from continuations to 
pre-continuations.

\todo[inline]{bisimilarity}

\begin{lemma}[Weak Bi-simulation between $ \mathcal{S}(\cdot) $ and $ 
\mathcal{D} $]
\label{thm:surely-monoidic-reduce}
For all cast representations $ C $, 
if $ C $ is surely \lazyD{} and monoidic,
$ s_1 \in \mathcal{D} $,
$ s_2 \in \mathcal{S}(C) $, and
$ s_1 \approx s_2 $, 
\begin{enumerate}
	\item If $ \judgeDBreduce{s_1}{s_3} $,
	then
	there exist $ s_5 \in \mathcal{D} $, $ s_4 \in \mathcal{S}(C) $,
	such that \begin{itemize}
		\item $ s_5 \approx s_4 $, and
		\item $ \judgeSreduce{C}{s_2}{s_4} $,
		\item $ \judgeDBreduceTrans{s_3}{s_5} $
	\end{itemize}
	\item If $ \judgeSreduce{C}{s_2}{s_4} $,
	then
	there exist $ s_3 \in \mathcal{D} $,
	such that \begin{itemize}
		\item $ s_3 \approx s_4 $
		\item $ \judgeDBreduceTrans{s_1}{s_3} $
	\end{itemize}
\end{enumerate}
\end{lemma}
\begin{proof}
	See the supplementary material.
\end{proof}

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
$ \mathcal{D} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and monoidic,
	\[
	\judgeDBeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{lemma}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
\end{proof}

\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
	$ \mathcal{D} $]
	\label{thm:surely-lazyD-correct}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{}
\[
\judgeDBeval{e}{o} \; \text{if and only if} \; 
\judgeSeval{C}{e}{o}
\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}.
\end{proof}

\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{D} $}
\label{sec:LDHC-correct}

To show that \lazyD\ HC is correct, we first show it is surely \lazyD, then 
uses the Theorem~\ref{thm:surely-lazyD-correct} to prove its correctness.

\figref{hc-applyCast} defines $ applyCast $, the last interface function.
We generalize shallow-consistency to middles and values ($ m \smile v $) in the 
natural way.
Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.

@@

\begin{lemma}[\lazyD{} Hyper-coercion is Surely \lazyD]
	\label{thm:hc-surely-lazyD}
\end{lemma}
\begin{proof}
	See the supplementary material.
\end{proof}

\begin{theorem}[\lazyD{} Hyper-coercion Respect $ \mathcal{D} $]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeDBeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:hc-surely-lazyD} and 
	Theorem~\ref{thm:surely-lazyD-correct}.
\end{proof}
